% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2016 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}

% Fonts
\usepackage[T1]{fontenc}
% \usepackage[urw-garamond]{mathdesign}
\usepackage{mathpazo}
\usepackage{microtype}
% \usepackage{textcomp}
% Set your name here
\def\name{Cyrus Omar}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {programming languages, computer science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1in,
  bottom=0.9in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.25em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.2em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}

% Place name at left
{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
  Computer Science and Engineering\\
  University of Michigan\\
  2260 Hayward Street\\
  Ann Arbor, MI 48109-2121
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  \textbf{Office}: 4773 Bob and Betty Beyster Building (BBB) \\
  \textbf{Email}: \href{mailto:comar@umich.edu}{\texttt{comar@umich.edu}} \\
  \textbf{Phone / Fax}: available by request\\
  \textbf{Webpage}: \href{https://web.eecs.umich.edu/~comar}{\texttt{https://web.eecs.umich.edu/\textasciitilde comar}} \\
  \textbf{Citizenship}: USA
\end{minipage}

% \section*{Employment}

% \begin{itemize}
% \item The Ohio State University, Department of Economics,
%   Assistant Professor, July 2010--present.
% \item Yale Center for Customer Insights,
%   Melville Blake '80 Visiting Summer Fellow,
%   2012.
% \item Duke University,
%   Research and Teaching Assistant,
%   2005--2010.
% \end{itemize}

% \subsection*{Duke University, Department of Economics}
%
% \begin{itemize}
% \item Research Assistant, Jacob Vigdor, Summer 2005--Summer 2006.
% \item Teaching Assistant, Ph.D. Microeconomic Analysis, Thomas Nechyba, Fall 2005.
% \item Teaching Assistant, Ph.D. Game Theory, Curtis Taylor, Spring 2006.
% \item Instructor, Microeconomics Qualifier Camp, Summer 2006.
% \item Research Assistant, Han Hong, Fall 2006--Spring 2007.
% \item Research Assistant, Aprajit Mahajan and Alessandro Tarozzi,
%   October--November 2006, March--June 2007.
% \item Research Assistant, Shakeeb Khan and Christopher Timmins,
%   March--June 2007.
% \item Teaching Assistant, Ph.D. Econometrics II, Shakeeb Khan,
%   Spring 2007.
% \item Research Assistant, Peter Arcidiacono, Patrick Bayer,
%   and Paul Ellickson, Fall 2007--Spring 2009.
% \item Research Assistant, Shakeeb Khan, Fall 2009--Spring 2010.
% \item Research Assistant, Aprajit Mahajan, July--September 2009.
% \end{itemize}

% \subsection*{North Carolina State University, Department of Mathematics}
%
% \begin{itemize}
% \item Research Assistant, Moody Chu and Robert Funderlic,
%   Spring 2003--Fall 2004.
% \item Mathematics Tutor, Academic Support Program for Student Athletes,
%   Summer 2001.
% \end{itemize}

% \subsection*{Colorado School of Mines,
%   Department of Mathematical and Computer Sciences}
%
% \begin{itemize}
% \item Research Assistant, Willy Hereman, Summer 2002.
% \end{itemize}

\section*{Employment}

\subsection*{University of Michigan}
\begin{itemize}
  \item \textbf{Assistant Professor} (Sep. 2019-present)
  \item Future of Programming Lab (FP Lab)
  \item Computer Science and Engineering (CSE) Division
  \item Electrical Engineering and Computer Science (EECS) Department
  \item College of Engineering (CoE)
\end{itemize}

\subsection*{University of Chicago}
\begin{itemize}
  \item \textbf{Postdoctoral Scholar} (Sep. 2017-Aug. 2019)
  \item Department of Computer Science
  \item Supervisor: Ravi Chugh
\end{itemize}

\subsection*{Carnegie Mellon University}
\begin{itemize}
  \item \textbf{Postdoctoral Scholar} (May. 2017-Aug. 2017)
  \item Computer Science Department
  \item Supervisor: Jonathan Aldrich
\end{itemize}


\section*{Education}

\subsection*{Carnegie Mellon University}

\begin{itemize}
  \item \textbf{Ph.D. in Computer Science} (Oct. 2010-May 2017)
        \begin{itemize}
          \item Thesis: \emph{Reasonably Programmable Syntax}
          \item Advisor: Jonathan Aldrich
                % \item Thesis Committee: Jonathan Aldrich, Robert Harper, Karl Crary, and Eric Van Wyk
                % \item Coursework: {Type Systems}, {Machine Learning}, {Optimizing Compilers for Modern Architectures}, {Advanced Operating Systems and Distributed Systems}, {Human Aspects of Software Development}, {Algorithms (Placed Out)}
        \end{itemize}
  \item Center for the Neural Basis of Cognition
        \begin{itemize}
          \item Graduate Training Program Certificate (Oct. 2010-May 2017)
          \item PhD Program in Neural Computation (Aug. 2008-Oct. 2010)
                %     % \item Coursework: {Computational Neuroscience Methods}, {Mathematical Neuroscience}, {Computational Models of Neural Systems}, {Systems Neuroscience}, {Applied Analysis}, {Time Series Analysis II}, {Cognitive Neuroscience}
        \end{itemize}
\end{itemize}

\subsection*{University of Illinois at Urbana-Champaign}
\begin{itemize}
  \item \textbf{B.S. in Computer Science}, 2008
  \item \textbf{B.S. in Molecular \& Cellular Biology}, 2008
\end{itemize}


\section*{Internships}
\subsection*{Los Alamos National Lab}
\begin{itemize}
  \item Synthetic Visual Cognition Group (May 2010-August 2010)
  \item Supervisor: Garrett Kenyon
\end{itemize}

\section*{Individual Awards}
\begin{enumerate}
  \item NSF CAREER Award
  \item {Alan J. Perlis SCS Graduate Teaching Award}
  \item DOE Computational Science Graduate Fellowship
  \item NSF Graduate Research Fellowship
  \item Inductee, University of Illinois Bronze Tablet
        % \item Duncan H. Lawrie Leadership Award %(2008)
        % \item Jeffrey P. Blahut Memorial Scholarship (2007)
        % \item Franz Hohn and J. P. Nash Scholarship
\end{enumerate}

\section*{Research}

\textit{Primary Research Area:} programming languages \\
\textit{Secondary Research Areas:} human-computer interaction, learning technology, artificial intelligence

\newcommand{\advisee}[1]{#1$^\dagger$}
$\dagger$ = advised during paper preparation

\begin{enumerate}[leftmargin=*, labelindent=6.5em, font=\bfseries]
  \item[POPL 2024] {Total Type Error Localization and Recovery with Holes}
  \begin{itemize}
    \item \advisee{E. Zhao}, \advisee{R. Maroof}, \advisee{A. Dukkipati}, \advisee{A. Blinn}, \advisee{Z. Pan}, \underline{C. Omar}
    \item \textit{Proc. ACM Program. Lang}, POPL
  \end{itemize}
  \item[VL/HCC 2023] {Gradual Structure Editing with Obligations}
  \begin{itemize}
    \item \advisee{D. Moon}, \advisee{A. Blinn}, \underline{C. Omar}
    \item \textit{IEEE Symposium on Visual Languages and Human-Centered Computing}
  \end{itemize}
  \item[OOPSLA 2023] {Live Pattern Matching with Typed Holes}
        \begin{itemize}
          \item \advisee{Y. Yuan}, \advisee{S. Guest}, \advisee{E. Griffis}, \advisee{H. Potter}, \advisee{D. Moon}, \underline{C. Omar}
          \item \textit{Proc. ACM Program. Lang.}, OOPSLA
        \end{itemize}
  \item[Onward! 2022] {Contextualized Programming Language Documentation}
        \begin{itemize}
          \item \advisee{H. Potter}, A. Madadi, R. Just, \underline{C. Omar}
          \item \textit{Proceedings of the 2022 ACM SIGPLAN International Symposium on New Ideas, New Paradigms, and Reflections on Programming and Software}
        \end{itemize}
  \item[VL/HCC 2022] {RustViz: Interactively Visualizing Ownership and Borrowing}
        \begin{itemize}
          \item \advisee{M. Almeida}, \advisee{G. Cole}, \advisee{K. Du}, \advisee{G. Luo}, \advisee{S. Pan}, \advisee{Y. Pan}, \advisee{K. Qiu}, \advisee{V. Reddy}, \advisee{H. Zhang}, \advisee{Y. Zhu}, \underline{C. Omar}
          \item \textit{IEEE Symposium on Visual Languages and Human-Centered Computing}
        \end{itemize}
  \item[VL/HCC 2022] {An Integrative Human-Centered Architecture for Interactive Programming Assistants}
        \begin{itemize}
          \item \advisee{A. Blinn}, \advisee{D. Moon}, \advisee{E. Griffis}, \underline{C. Omar}
          \item \textit{IEEE Symposium on Visual Languages and Human-Centered Computing} 
        \end{itemize}
  \item[PLDI 2021] {Filling Typed Holes with Live GUIs}
        \begin{itemize}
          \item \underline{C. Omar}, \advisee{D. Moon}, \advisee{A. Blinn}, I. Voysey, N. Collins, and R. Chugh
          \item \textit{42nd ACM SIGPLAN International Conference on Programming Language Design and Implementation}
        \end{itemize}
  \item[HATRA 2020] Hazel Tutor: Guiding Novices Through Type-Driven Development
        \begin{itemize}
          \item \advisee{H. Potter} and \underline{C. Omar}
          \item \textit{1st Workshop on Human Aspects of Types and Reasoning Assistants}
        \end{itemize}
  \item[ICFP 2020] {Program Sketching with Live Bidirectional Evaluation}
        \begin{itemize}
          \item J. Lubin, N. Collins, \underline{C. Omar}, and R. Chugh
          \item \textit{Proc. ACM Program. Lang.} 4, ICFP, Article 109
        \end{itemize}
  \item[POPL 2019] {Live Functional Programming with Typed Holes}
        \begin{itemize}
          \item \underline{C. Omar}, I. Voysey, R. Chugh and M. Hammer
          \item \textit{Proc. ACM Program. Lang.} 3, POPL, Article 14
        \end{itemize}
  \item[ICFP 2018] {Reasonably Programmable Literal Notation}
        \begin{itemize}
          \item \underline{C. Omar} and J. Aldrich
          \item \textit{Proc. ACM Program. Lang.} 2, ICFP, Article 106
        \end{itemize}
  \item[SNAPL 2018] Toward Semantic Foundations for Program Editors
        \begin{itemize}
          \item \underline{C. Omar}, I. Voysey, M. Hilton, J. Sunshine, C. Le Goues, J. Aldrich and M. Hammer
          \item \textit{2nd Symposium on Advances in Programming Languages} 
        \end{itemize}
  \item[POPL 2017] {Hazelnut: A Bidirectionally Typed Structure Editor Calculus}
        \begin{itemize}
          \item \underline{C. Omar}, I. Voysey, M. Hilton, J. Aldrich and M. Hammer
          \item \textit{44th ACM SIGPLAN Symposium on Principles of Programming Languages} 
        \end{itemize}
  \item[GPCE 2016] {Programmable Semantic Fragments: The Design and Implementation of \texttt{typy}}
        \begin{itemize}
          \item \underline{C. Omar} and J. Aldrich.
          \item \textit{15th ACM SIGPLAN International Conference on Generative Programming: Concepts \& Experiences}
        \end{itemize}
  \item[SAC 2015] Composable and Hygienic Typed Syntax Macros
        \begin{itemize}
          \item \underline{C. Omar}, C. Wang and J. Aldrich
          \item \textit{30th ACM Symposium on Applied Computing}
        \end{itemize}
  \item[ECOOP 2014] {Safely Composable Type-Specific Languages}
        \begin{itemize}
          \item \underline{C. Omar}, D. Kurilova, L. Nistor, B. Chung, A. Potanin and J. Aldrich.
          \item \textit{28th European Conference on Object-Oriented Programming}
          \item \textbf{Distinguished Paper Award}
        \end{itemize}
  \item[PSP 2014] Statically Typed String Sanitation Inside a Python
        \begin{itemize}
          \item N. Fulton, \underline{C. Omar} and J. Aldrich
          \item \textit{1st International Workshop on Privacy and Security in Programming} {\textbf{(PSP 2014)}}
          \item \textbf{Best Paper Award}
        \end{itemize}
  \item[ICSE 2014] Collaborative Infrastructure for Test-Driven Scientific Model Validation
        \begin{itemize}
          \item \underline{C. Omar}, J. Aldrich and R. Gerkin
          \item \textit{47th International Conference on Software Engineering}
          \item New Ideas \& Emerging Results Track (18\% acceptance rate)
        \end{itemize}
  \item[IWACO 2014] Language-Based Architectural Control
        \begin{itemize}
          \item J. Aldrich, \underline{C. Omar}, A. Potanin and D. Li
          \item \textit{6th International Workshop on Aliasing, Capabilities and Ownership}
        \end{itemize}
  \item[GlobalDSL 2013] Type-Directed, Whitespace-Delimited Parsing for Embedded DSLs
        \begin{itemize}
          \item \underline{C. Omar}, B. Chung, D. Kurilova, A. Potanin and J. Aldrich
          \item \textit{2013 International Workshop on the Globalization of Domain-Specific Languages}
        \end{itemize}
  \item[ICSE 2012] {Active Code Completion}.
        \begin{itemize}
          \item \underline{C. Omar}, Y. Yoon, T. D. LaToza and B. A. Myers
          \item \textit{45th International Conference on Software Engineering}
        \end{itemize}
  \item[J. Neuro. 2012] {Neural correlation is stimulus modulated by feedforward inhibitory circuitry}
        \begin{itemize}
          \item J. W. Middleton, \underline{C. Omar}, B. Doiron and D. J. Simons
          \item \textit{Journal of Neuroscience} 32(2):506--18
        \end{itemize}
  \item[IJHCI 2011] A Feedback Information-Theoretic Approach to the Design of Brain-Computer Interfaces.
        \begin{itemize}
          \item  \underline{C. Omar}, A. Akce, M. Johnson, T. Bretl, R. Ma, E. Maclin, M. McCormick and T. Coleman
          \item \textit{International Journal of Human-Computer Interaction}, 27:1, 5--23
        \end{itemize}
  \item[ACC 2008] Policies for neural prosthetic control: initial experiments with a text interface
        \begin{itemize}
          \item \underline{C. Omar}, M. Johnson, T. Bretl and T. Coleman
          \item \textit{2008 American Control Conference} 
        \end{itemize}
  \item[ICASSP 2008] Querying the user properly for high-performance brain machine interfaces: recursive estimation, control and feedback information theoretic perspectives
        \begin{itemize}
          \item \underline{C. Omar}, M. Johnson, T. Bretl and T. Coleman
          \item \textit{2008 IEEE International Conference on Acoustics, Speech, and Signal Processing}
        \end{itemize}
  \item[IJCNN 2008] Shedding the weights: more with less
        \begin{itemize}
          \item T. Achler, \underline{C. Omar} and E. Amir
          \item \textit{2008 International Joint Conference on Neural Networks}
        \end{itemize}

\end{enumerate}

% \subsection*{Working Drafts}

% \begin{enumerate}[resume]
% \item Reasonably Programmable Syntax
%   \begin{itemize}
%     \item \underline{C. Omar} and J. Aldrich
%     \item Dissertation and accompanying journal paper in preparation
%     \item \textbf{2nd Place, ICFP 2015 Graduate Student Research Competition}
%   \end{itemize}
% \item Hazelnut Live: Semantic Foundations for Evaluating Incomplete Programs
%   \begin{itemize}
%     \item \underline{C. Omar}, I. Voysey, M. Hilton, J. Aldrich and M. Hammer
%   \end{itemize}
% \item Statistical Models of Typed Syntax Trees
%   \begin{itemize}
%     \item \underline{C. Omar}, S. Joshi and F. Cruz
%     \item \textbf{3rd Place, SPLASH 2014 Graduate Student Research Competition}
%   \end{itemize}
% \item Tidy: A Modularly Programmable Bidirectionally Typed Translation Semantics
%   \begin{itemize}
%     \item \underline{C. Omar} and J. Aldrich
%   \end{itemize}
% \end{enumerate}

\section*{Selected Talks}
\begin{enumerate}
  \item Invited talk, University of Washington, Sep 2023
  \item Invited talk, IFIP Working Group 2.3 (Language Design), Jan 2023
  \item Invited talk, Ink \& Switch, May 2022
  \item Invited talk, University of Toledo, Feb 2022
  \item Invited talk, University of Washington, December 2021
  \item Invited talk, Strumenta Community, December 2021
  \item Invited talk, UC Berkeley, October 2021
  \item Invited talk, UC San Diego, Summer 2021
  \item Invited talk, Hackworth Ltd., Summer 2021
  \item Invited talk, Webflow, Summer 2021
  \item Invited Talk, PPIG 2020
  \item Accepted talk, Midwest PL Summit 2019
  \item Accepted talk, TyDe 2019
  \item Invited talk, Chicago Functional Programming Meetup + Reason Meetup (joint talk), 2018
  \item Accepted talk, LIVE 2018
  \item Accepted talk, META 2018
  \item Invited talk, CMU Principles of Programming Seminar, 2018
  \item Accepted talk, Strange Loop, 2018
  \item Invited talk, Ink \& Switch, 2018
  \item Invited talk, Purdue University, 2017
  \item Invited talk, TU Darmstadt, 2017
  \item Accepted talk, LIVE 2017
  \item Invited talk, HARC (Y Combinator Research), 2016
        % \item Modularly Programmable Type Structure
        %   \begin{itemize}
        %     \item Invited talk, TU Darmstadt (scheduled January 2017)
        %   \end{itemize}
        % \item Hazel: Semantic Foundations for Interactive Programming Tools
        %   \begin{itemize}
        %     \item Invited talk, HARC (Y Combinator Research), 2016
        %     \item IBM Programming Languages Day, 2016
        %   \end{itemize}
        % \item Modular Syntax 
        %   \begin{itemize}
        %     \item Parsing@SLE Workshop, 2015
        %   \end{itemize}
        % \item Modularly Programmable Syntax and Type Structure
        %   \begin{itemize}
        %     \item CMU Principles of Programming Seminar, June 2015
        %   \end{itemize}
        % \item Composable and Hygienic Typed Syntax Macros
        %   \begin{itemize}
        %     \item {Domain-Specific Language Design and Implementation Workshop (DSLDI 2014)}
        %   \end{itemize}
        % \item Active Typechecking and Translation
        %   \begin{itemize}
        %     \item Domain-Specific Language Design and Implementation Workshop (DSLDI 2013)
        %     \item nVidia GPU Technology Conference 2013
        %   \end{itemize}
        % \item Open Science
        %   \begin{itemize}
        %     \item Joint talk with Shreejoy Tripathy
        %     \item Center for the Neural Basis of Cognition Brain Bag
        %   \end{itemize}
        % \item Sound, Usable and Flexible Foundations for Scientific and High-Performance Languages and Tools 
        %   \begin{itemize}
        %     \item SIAM Conference on Parallel Processing for Scientific Computing (PP 2012)
        %   \end{itemize}
        % \item End-User Programming by Scientists
        %   \begin{itemize}
        %     \item Lecture, Human Aspects of Software Development (Spring 2011)
        %   \end{itemize}

        % \item How do people naturally think about computation?
        %   \begin{itemize}
        %     \item Lecture, Human Aspects of Software Development (Spring 2011)
        %   \end{itemize}
\end{enumerate}

% \section*{Selected Press Coverage}
% % \subsubsection*{Type-Specific Languages in Wyvern}
% \begin{enumerate}
%   \item GigaOm (Aug. 7, 2014)
%   \item Motherboard (Aug. 8, 2014)
%   \item ACM TechNews (Aug. 11, 2014)
%   \item Gizmodo (Aug. 11, 2014)
%   \item SD Times (Aug. 13, 2014)
%   \item ITBusinessEdge (Aug. 14, 2014)
%   \item The Tartan (Aug. 24, 2014)
% \end{enumerate}

% \subsection*{Scientific Software}
%
% \begin{itemize}
% \item \href{http://jblevins.org/research/pdest}{PDESolutionTester},
%   A Mathematica program for the symbolic verification of exact solutions
%   of nonlinear partial differential equations,
%   with Jeff Heath and Willy Hereman (2002).
% \item \href{http://jblevins.org/research/dfbr}{DFBR},
%   A Stata program for distribution-free estimation of heteroskedastic
%   binary response models,
%   with Shakeeb Khan (2009).
% \end{itemize}


\section*{Teaching}
\subsection*{University of Michigan}
\begin{itemize}
  \item \textbf{EECS 490: Programming Languages}
        \begin{itemize}
          \item Winter 2020, Fall 2020, Winter 2021, Fall 2021, Winter 2022, Fall 2022, Winter 2023, Fall 2023
        \end{itemize}
  \item \textbf{EECS 598-015: User Interfaces for Programming Languages}
        \begin{itemize}
          \item Fall 2019
        \end{itemize}
\end{itemize}

\subsection*{Carnegie Mellon University}
\begin{itemize}
  \item \textbf{15-312: Principles of Programming Languages}
        \begin{itemize}
          \item Spring 2013, Head TA, with Prof. Robert Harper
        \end{itemize}
  \item \textbf{15-150: Functional Programming}
        \begin{itemize}
          \item Fall 2011, Head TA, with Prof. Dan Licata
        \end{itemize}
\end{itemize}


\section*{Advising}

\subsection*{University of Michigan}
\begin{itemize}
  \item Postdocs and Research Scientists (advising period; subsequent placement)
        \begin{enumerate}
          \item Michael D. Adams (Fall 2019-Winter 2021; Assistant Professor at Yale-NUS)
        \end{enumerate}
  \item PhD Students (advised)
        \begin{enumerate}
          \item Matthew Keenan (Fall 2023-present)
          \item Andrew Blinn (Fall 2020-present)
          \item Eric Griffis (Fall 2020-Summer 2022)
          \item David Moon (Fall 2019-present)
        \end{enumerate}
  \item PhD Students (committee membership)
        \begin{enumerate}
          \item Xiaoying Pu (CSE, 2022)
          \item April Wang (School of Information, 2023)
        \end{enumerate}
  \item Masters Students
        \begin{enumerate}
          \item Karan Anand (Summer 2023-present)
          \item Junwei Zhou (Winter 2023-present)
          \item Matthew Ruiz (Winter 2023-present)
          \item Alan Yang (Winter 2023-present)
          \item Jonathan Lam (MS student at Cooper Union, Fall 2021-Summer 2022; industry position)
          \item Priya Thanneermalai (Summer 2021-Fall 2021; industry position)
          \item Soo Yeon (Sean) Lee (Winter 2020-Summer 2021; industry position)
          \item Hannah Potter (Fall 2019-Summer 2021; PhD student at University of Washington)
          \item Erin Deutschman (Winter 2020-Summer 2021; industry position)
        \end{enumerate}
  \item Undergraduates (the following lists students who went on to PhD programs only)
        \begin{enumerate}
          \item Luoxi (Rosie) Meng (Winter 2022-Fall 2022; PhD student at UCSD)
          \item Siyuan He (Winter 2020-Summer 2021; PhD student at Purdue University)
          \item Yuning Wang (Winter 2020-Summer 2021; PhD student at Rutgers University)
          \item Yongwei Yuan (Fall 2019-Summer 2020; PhD student at Purdue University)
          \item Ke Du (Fall 2019-Summer 2020; PhD student at UIC)
                % \item Yunsoo Kim (Winter 2020-present)
                % \item Yuning Wang (Winter 2020-present)
                % \item Zhiyi Pan (Winter 2020-present)
                % \item Dibyadarshi Dash (Winter 2020-present)
                % \item Marcelo Almeida (Winter 2020-present)
                % \item Nicholas Wilson (Winter 2020-present)
                % \item Erin Deutschman (Winter 2020-present)
                % \item Soo Yeon Lee (Winter 2020-present)
                % \item Utkarsh Mehta (Winter 2020-present)
                % \item Siyuan He (Winter 2020-present)
                % \item Yongwei Yuan (Fall 2019-present) (now a PhD student at Purdue University)
                % \item Benjamin Carney (Winter 2020-Summer 2020)
                % \item Gabriel Luo (Fall 2019-Fall 2020)
                % \item Ke Du (Fall 2019-Winter 2020)
                % \item Qiran Li (Fall 2019-Winter 2020)
                % \item Mengjing Xu (Winter 2020-Fall 2020)
                % \item Yingying Zhu (Winter 2020-Fall 2020)
                % \item Yuanhao Meng (Winter 2019-Summer 2020)
                % \item Aditya Koneru (Winter 2020-Summer 2020)
                % \item Prashant Shankar (Winter 2020-Summer 2020)
          \item[...] (80+ other undergraduate research students as of Aug 1, 2021, see lab website for full listing)
        \end{enumerate}
\end{itemize}

\subsection*{Prior to Faculty Position}

\begin{itemize}
  % \item PhD Students (year; faculty advisor)
  %   \begin{enumerate}
  %     \item David Moon (2018-2019; Matthew A. Hammer)
  %     \item Nick Collins (2018-present; Ravi Chugh)
  %   \end{enumerate}
  \item Undergraduates (year; faculty advisor; subsequent placement)
        \begin{enumerate}
          % \item Ian Voysey (2016-present; -; Staff Programmer, Carnegie Mellon University)
          \item Charles Chamberlain (2017-present; -; Jane Street Capital)
          \item Andrew Benson (2016; Jonathan Aldrich; Facebook)
          \item Chenglong Wang (2015; Jonathan Aldrich; PhD student, University of Washington)
          \item Benjamin Chung (2014; Jonathan Aldrich; PhD student, Northeastern University)
          \item Nathan Fulton (2012; Jonathan Aldrich; PhD student, Carnegie Mellon University)
          \item Michael Rule (2009; Nathan Urban; PhD student, Brown University)
        \end{enumerate}
\end{itemize}




\section*{External Service}
\begin{enumerate}
  \item Program Committee, OOPSLA 2024
  \item Steering Committee Co-chair, MWPLS 2024-2025
  \item Reviewer, CHI 2024
  \item Reviewer, Wiley Publishing 2023
  \item Reviewer, ACM Transactions on Programming Languages and Systems (TOPLAS), 2023
  \item Panelist, Programming Languages Mentoring Workshop (PLMW) at ICFP 2023
  \item Program Committee, SPLASH-E 2023
  \item Co-chair, Midwest PL Summit (MWPLS) 2023
  \item Steering Committee Chair, TyDe (2022-2024)
  \item Program Committee, PLDI 2023
  \item Program Committee, ECOOP 2023
  \item Program Committee, VL/HCC 2023
  \item Program Committee, HATRA 2023
  \item Program Committee, IFL 2023
  \item Program Committee and Area Chair (Brave New Ideas and Pearls), ECOOP 2023
  \item Panelist, NSF SHF Core Panel 2023
  \item Panelist, European Research Council (ERC) 2023
  \item External Reviewer, UIST 2023
  \item Reviewer, MIT Press 2022
  \item Mentor, PLMW at SPLASH 2022
  \item Program Committee, IFL 2022
  \item Program Committee, HATRA 2022
  \item Program Committee, SPLASH Student Research Competition (SPLASH SRC) 2022
  \item Program Committee, VL/HCC 2022
  \item Program Committee, HATRA 2021
  \item External Reviewer, UIST 2021
  \item Program Committee, ICFP 2021
  \item Program Committee, LIVE 2020
  \item Program Committee, HATRA 2020
  \item Co-Chair, Midwest PL Summit (MWPLS) 2020 [canceled due to COVID]
  \item Co-Chair, Type-Driven Development (TyDe) workshop at ICFP 2020
  \item External Review Committee, ICFP 2020
  \item Student Research Competition Committee, ICFP 2020
  \item Program Committee, HATRA 2020
  \item Program Committee, Onward! Papers 2019
  \item Program Committee, LIVE 2019
  \item Program Committee, META 2019
  \item Program Committee, ML Family Workshop 2019
  \item Artifact Evaluation Committee, ICFP 2019
  \item Program Committee, LIVE 2018
  \item Program Committee, SPLASH Student Research Competition 2018
  \item Referee, Journal of Visual Languages and Computing 2018
  \item Program Committee, META 2017
  \item Publicity Chair and Program Committee, GPCE 2017
  \item Program Committee, DSLDI 2015
  \item Artifact Evaluation Committee, ECOOP 2015
        % \item CMU CSD Graduate Admissions Committee, 2013
        % \item CMU CNBC Social Committee Chair, 2011
\end{enumerate}

\section*{Internal Service}
\begin{enumerate}
  \item Member, CSE Diversity Committee, Fall 2019-present
        \begin{enumerate}
          \item External engagement (ongoing)
          \item Coordinated engagement with MS Admissions (ongoing)
          \item Led development of the CSE Departmental Broadening Participation in Computing (BPC) Plan
          \item Participated in the development of the Summer 2020 Graduate Student Individual Check-In program
          \item Wrote Faculty Recruiting section of DEI Committee Annual Report (each year)
        \end{enumerate}
  \item Member, CSE Hosting Committee, Fall 2020-present
  \item Organizer, CSE New Faculty Handbook project, Fall 2022-present
  \item Organizer, MPLSE (Michigan PL + SE) Group, Fall 2019-present
  \item Proposal Reviewer, Michigan Institute for Computational Discovery and Engineering (MICDE), 2023
  \item Mentor, Girls Encoded / Explore CS Research program, Winter 2021
  \item Mentor, African Undergraduate Research Adventure (AURA) program, Summer 2021
  \item Mentor, Summer Undergraduate Research in Engineering (SURE) program, Summer 2020-2023
\end{enumerate}


\section*{Funding}

\begin{itemize}
  \item Michigan Engineering Seeding to Accelerate Research Themes (START):\\
        Interactively Deriving Formal Proofs (2023-2024)
        \begin{itemize}
          \item Co-PI: Jean-Baptiste Jeannin
          \item Total: \$30,000, My portion: \$15,000
        \end{itemize}
  \item CSE Course Development Funding for EECS 490
        \begin{itemize}
          \item Total: \$7,280
        \end{itemize}
  \item NSF support for Midwest Programming Languages Summit (2023-2026)
        \begin{itemize}
          \item Total: \$15,000
        \end{itemize}
  \item Provost Early Tenure Track Faculty Research Support Initiative (2023)
        \begin{itemize}
          \item Total: \$3,000
        \end{itemize}
  \item CAREER: Live and Direct Programming Environments (2023-2028)
        \begin{itemize}
          \item Total: \$550,000
          \item NSF Cloudbank Supplement: \$6,000
        \end{itemize}
  \item Infrastructure for Developing Interactive Rust Learning Material (2022-2023)
        \begin{itemize}
          \item Futurewei via Portland State University (subcontract)
          \item Total: \$52,000
        \end{itemize}
  \item College of Engineering COVID Support Funding (2022)
        \begin{itemize}
          \item Total: \$50,000
        \end{itemize}
  \item NSF Small: Semantic Foundations for Hole-Driven Development (2018-2021)
        \begin{itemize}
          \item Total: \$500,000 / My portion: \$192,635 (subcontract from CU Boulder)
        \end{itemize}
\end{itemize}

% \section*{Professional References}

% \begin{enumerate}
% % \item \underline{C. Omar} and C. Le Goues. Statistically Ranked, Type-Aware Action Suggestions. \textit{POPL 2018}. 
% % \item \underline{C. Omar} and J. Aldrich. Reasonably Programmable Syntax. \textit{ICFP 2017}. 
% % \item \underline{C. Omar}, I. Voysey, M. Hilton, J. Aldrich and M. Hammer. Hazelnut Live: Semantic Foundations for Evaluating Incomplete Programs. \textit{ICFP 2017}.
% % \item \underline{C. Omar} and J. Aldrich. Tidy: A Modularly Programmable Bidirectionally Typed Translation Calculus. \textit{ICFP 2017}. 
% \item {Prof. Jonathan Aldrich}
%   \begin{itemize}
%     \item Professor, Carnegie Mellon University
%     \item \url{jonathan.aldrich@cs.cmu.edu}
%   \end{itemize}
% \item {Prof. Ravi Chugh}
%   \begin{itemize}
%     \item Assistant Professor, University of Chicago
%     \item \url{rchugh@cs.uchicago.edu}
%   \end{itemize}
% \item {Prof. Robert Harper}
%   \begin{itemize}
%     \item Professor, Carnegie Mellon University
%     \item \url{rwh@cs.cmu.edu}
%   \end{itemize}
% \item {Prof. Matthew A. Hammer}
%   \begin{itemize}
%     \item Assistant Professor, University of Colorado Boulder
%     \item \url{matthew.hammer@colorado.edu}
%   \end{itemize}
% \end{enumerate}

% \section*{Scientific Software}
% \begin{itemize}
%   \item Graphite
%   \item Wyvern (Scala)
%   \item Wyvern (Java)
%   \item SciUnit
%   \item typy
%   \item HZ
%   \item Hazelnut mechanization
% \end{itemize}
% \section*{Talks and Posters}
% \subsection*{2016}
% \begin{enumerate}
%   \item \textit{IBM Programming Languages Day}
% \end{enumerate}

% \subsection*{2015}
% \begin{enumerate}
%   \item \textit{ICFP 2015 Student Research Competition} (poster and talk)
%   \item \textit{CMU POP Seminar}
%   \item \textit{Parsing@SLE Workshop 2015}
%   \item \textit{SAC 2015}
% \end{enumerate}

% \subsection*{2014}
% \begin{enumerate}
%   \item \textit{ICSE 2014}
% \end{enumerate}
% \subsection*{2013}
% \begin{enumerate}
%   \item \textit{Workshop on Domain-Specific Language Design and Implementation}
%   \item \textit{International Workshop on Globalization of Domain-Specific Languages}
%   \item \textit{Parsing@SLE Workshop 2013}
%   \item \textit{nVidia GPU Technology Conference}
%   \item \textit{SPLASH 2013 Student Research Competition} (poster and talk)
% \end{enumerate}
% \section*{Press Coverage}
% \begin{enumerate}
%   \item Hacker News
%   \item GigaOm
%   \item Reddit Programming
%   \item Motherboard
%   \item ACM Technews
%   \item Slashdot
%   \item Gizmodo
%   \item SDTimes
%   \item ITBusinessEdge
%   \item 
% \end{enumerate}
% Footer
\bigskip
{\small Last updated: \today}

\end{document}